Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a structure $\T$ of \cite{aak+12}. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ with {\em weight} $x_2$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $P$, search $\T$ to determine if any interval in $S_\ell$ contains the value $x$. If so, point $p$ is covered by at least one rectangle in $R$; otherwise, it is not. The overall running time is $O(n \log n)$.

>>>>

Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a structure $\T$ of \cite{aak+12}. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ with {\em weight} $x_2$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $P$, search $\T$ to determine the maximum weight $w$ of all the intervals in $S_\ell$ containing the value $x_1$. If $w \ne -\infty$, we output $(h, p)$ where the point $p$ is defined in a way depending on $w$: if $w \le x_2$, then $p = (w, y)$; otherwise $p = (x_2, y)$. The overall running time is $O(n \log n)$.
